\hypertarget{multinational-transfer-pricing-and-taxation.}{%
\subsection{Multinational transfer pricing and
taxation.}\label{multinational-transfer-pricing-and-taxation.}}

\hypertarget{us-subsidiary}{%
\subsection{US subsidiary}\label{us-subsidiary}}

\begin{itemize}
\tightlist
\item
  Vik-Giger Corporation, headquartered in the U.S., manufactures
  state-of-the-art milling machines.
\item
  It has two marketing subsidiaries, one in Brazil and one in
  Switzerland, that sell its products.
\item
  Vik-Giger is considering building one new machine, at a cost of
  \$500,000.
\item
  There is no market for the equipment in the United States.
\end{itemize}

\hypertarget{brazilian-subsidiary}{%
\subsection{Brazilian subsidiary}\label{brazilian-subsidiary}}

\begin{itemize}
\tightlist
\item
  The equipment can be sold in Brazil for \$1,000,000, but the Brazilian
  subsidiary would incur transportation and modification costs of
  \$200,000.
\end{itemize}

\hypertarget{swiss-subsidiary}{%
\subsection{Swiss subsidiary}\label{swiss-subsidiary}}

\begin{itemize}
\tightlist
\item
  Alternatively, the equipment can be sold in Switzerland for \$950,000,
  but the Swiss subsidiary would incur transportation and modification
  costs of \$250,000.
\end{itemize}

\hypertarget{decision}{%
\subsection{Decision}\label{decision}}

\begin{itemize}
\tightlist
\item
  The U.S. company can sell the equipment either to its Brazilian
  subsidiary or to its Swiss subsidiary but not to both.
\item
  Vik-Giger Corporation and its subsidiaries operate in a very
  decentralized manner. Managers in each company have considerable
  autonomy, with each division manager interested in maximizing his or
  her own division's income.
\end{itemize}

\hypertarget{question-1}{%
\subsection{Question 1:}\label{question-1}}

\begin{itemize}
\tightlist
\item
  From the viewpoint of Vik-Giger and its subsidiaries taken together,
  should Vik-Giger Corporation manufacture the equipment?

  \begin{itemize}
  \item
    \begin{enumerate}
    \def\labelenumi{(\alph{enumi})}
    \tightlist
    \item
      If it does, where should it sell the equipment to maximize
      corporate operating income?
    \end{enumerate}
  \item
    \begin{enumerate}
    \def\labelenumi{(\alph{enumi})}
    \setcounter{enumi}{1}
    \tightlist
    \item
      What would the operating income for Vik-Giger and its subsidiaries
      be from the sale? Ignore any income tax effects.
    \end{enumerate}
  \end{itemize}
\end{itemize}

\hypertarget{question-1-1}{%
\subsection{Question 1:}\label{question-1-1}}

To answer this question just calculate the operating income that
Vik-Giger gets in either case.

\hypertarget{option-1-sell-to-the-swiss}{%
\subsection{\texorpdfstring{\textbf{Option 1: Sell to the
Swiss}}{Option 1: Sell to the Swiss}}\label{option-1-sell-to-the-swiss}}

\begin{longtable}[]{@{}lc@{}}
\toprule\noalign{}
Description: & Amount \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Manufacturing Cost (US) & (500,000) \\
Transport etc. Cost & (250,000) \\
Sale in Swiss mkt. & 950,000 \\
\textbf{Vik-Giger Operating Income:} & \textbf{200,000} \\
\end{longtable}

\emph{Note that the Swiss department sees this as 700,000 of operating
income, and the US department sees this as a 500,000 operating loss.}

\hypertarget{option-2-sell-to-the-brazilians}{%
\subsection{\texorpdfstring{\textbf{Option 2: Sell to the
Brazilians}}{Option 2: Sell to the Brazilians}}\label{option-2-sell-to-the-brazilians}}

\begin{longtable}[]{@{}lc@{}}
\toprule\noalign{}
Description: & Amount \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Manufacturing Cost (US) & (500,000) \\
Transport etc. Cost & (200,000) \\
Sale in Brazilian mkt. & 1,000,000 \\
\textbf{Vik-Giger Operating Income:} & \textbf{300,000} \\
\end{longtable}

\emph{Note that the Brazilian department see this as 800,000 operating
income, and the US department sees this as a 500,000 operating loss.}

Vik-Giger prefers to sell in Brazil.

\hypertarget{question-2}{%
\subsection{Question 2:}\label{question-2}}

\begin{itemize}
\tightlist
\item
  What range of transfer prices will result in achieving the actions
  determined to be optimal in requirement 1? Explain your answer.
\end{itemize}

\hypertarget{consider-the-following-status-quo}{%
\subsection{\texorpdfstring{Consider the following \emph{status
quo}:}{Consider the following status quo:}}\label{consider-the-following-status-quo}}

\hypertarget{brazil}{%
\subsection{1. Brazil}\label{brazil}}

\begin{itemize}
\tightlist
\item
  The Brazilian department wants to sell the machine in their market,
  and capture 800,000 of operating income. This is what shareholders of
  the combined entity also prefer as they get 300,000 operating income.
\end{itemize}

\hypertarget{switzerland}{%
\subsection{2. Switzerland}\label{switzerland}}

\begin{itemize}
\tightlist
\item
  The Swiss department also wants to sell the machine in their market,
  and capture 750,000 of operating income. This is sub-optimal from the
  perspective of the combined entity as they can capture more operating
  income by selling in the Brazilian market.
\end{itemize}

\hypertarget{us}{%
\subsection{3. US}\label{us}}

\begin{itemize}
\tightlist
\item
  The manufacturing division in the US would prefer not to produce the
  product in either case as they only stand to loose 500,000.
\end{itemize}

\hypertarget{what-we-need-from-the-transfer-price}{%
\subsection{What we need from the transfer
price:}\label{what-we-need-from-the-transfer-price}}

Vik-Giger must centralize the decision, or choose a transfer price at
which (1) the US division agrees to produce, (2) the Brazilian division
is willing to transport and market the machine, and (3) the Swiss
division prefers not to transport and market the machine.

\hypertarget{we-can-use-a-negotiation-to-solve-this-problem}{%
\subsection{We can use a negotiation to solve this
problem:}\label{we-can-use-a-negotiation-to-solve-this-problem}}

\begin{itemize}
\tightlist
\item
  Imagine that Vik-Giger headquarters sends the three division CEOs to a
  resort in the Aleutian Islands (where it is cold so they will stay
  inside and negotiate) and asks them to choose a transfer price.
\end{itemize}

\hypertarget{the-us-division-decides-to-run-a-simple-auction}{%
\subsection{The US division decides to run a simple
auction:}\label{the-us-division-decides-to-run-a-simple-auction}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The US set the reserve at 500,000 as this is their cost.
\item
  Switzerland drops out of the bidding at 700,000 as they start to loose
  money beyond this point.
\item
  Brazil's winning bid is 700,000, this is the low end of the range of
  transfer prices that yield the solution that headquarters wants.
\end{enumerate}

\hypertarget{a-few-notes}{%
\subsection{A few notes:}\label{a-few-notes}}

\begin{itemize}
\tightlist
\item
  We are assuming that all of the costs quoted in this problem cover
  opportunity costs.
\item
  \textbf{Vik-Giger can get the optimal choice and remain
  decentralized.} They only need to require a transfer price, they don't
  need to centralize the choice of the transfer price.
\end{itemize}

\hypertarget{the-upper-end-of-the-range}{%
\subsection{The upper end of the
range:}\label{the-upper-end-of-the-range}}

\begin{itemize}
\tightlist
\item
  Both Brazil and the US will agree to transfer prices above 700,000,
  with the US pushing for higher transfer prices and Brazil pushing for
  lower prices.
\item
  We don't know enough to predict what the departments will actually
  agree to, though if they use an auction the transfer price will be
  very close to the price at which the Swiss drop out.
\item
  Brazil will drop out of the bidding at 800,000 so this is the top of
  the range.
\end{itemize}

\hypertarget{question-3}{%
\subsection{Question 3:}\label{question-3}}

\begin{itemize}
\tightlist
\item
  The effective income tax rates for this transaction follow: 40\% in
  the United States, 60\% in Brazil, and 15\% in Switzerland. The tax
  authorities in the three countries are uncertain about the cost of the
  intermediate product and will allow any transfer price between
  \$500,000 and \$700,000. If Vik-Giger and its subsidiaries want to
  maximize after-tax operating income:

  \begin{itemize}
  \item
    \begin{enumerate}
    \def\labelenumi{(\alph{enumi})}
    \tightlist
    \item
      should the equipment be manufactured and
    \end{enumerate}
  \item
    \begin{enumerate}
    \def\labelenumi{(\alph{enumi})}
    \setcounter{enumi}{1}
    \tightlist
    \item
      where and at what price should it be transferred?
    \end{enumerate}
  \end{itemize}
\end{itemize}

\hypertarget{optimal-transfer-pricing-in-the-presence-of-taxes}{%
\subsection{Optimal Transfer Pricing In the Presence of
Taxes}\label{optimal-transfer-pricing-in-the-presence-of-taxes}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  Now the transfer price is no longer being used primarily for
  information and incentives.
\item
  The transfer price is now used to locate income in low tax regimes.
\end{enumerate}

Let's consider our two options.

\hypertarget{option-1-sell-in-the-swiss-market}{%
\subsection{Option 1: Sell in the Swiss
market}\label{option-1-sell-in-the-swiss-market}}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2763}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2895}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.0263}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2632}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.1447}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Swiss Income (15\%)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Amount
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
US Income (40\%)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Amount
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Transfer Price & (500,000) & & Manufacturing Cost & (500,000) \\
Transport Cost & (250,000) & & Transfer Price & 500,000 \\
Sale Price & 950,000 & & & \\
\textbf{Swiss PTOI} & \textbf{200,000} & & \textbf{US PT/ATOI} &
\textbf{0} \\
Tax & (200,000\(\times\).15) & & & \\
\textbf{V-G ATOI} & \textbf{170,000} & & & \\
\end{longtable}

\hypertarget{note-the-following}{%
\subsection{Note the following:}\label{note-the-following}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The Swiss and the headquarters see the same after tax income numbers.
  The Swiss will prefer lower transfer prices, but the US will not
  agree, and the tax authorities will not permit it.
\item
  We are ignoring the ability to carry forward tax losses.
\item
  The US will agree to produce at this amount (it covers their
  opportunity cost).
\item
  This transfer price moves as much income as possible out of the US
  into Switzerland.
\end{enumerate}

\hypertarget{option-2-sell-in-the-brazilian-market}{%
\subsection{Option 2: Sell in the Brazilian
Market:}\label{option-2-sell-in-the-brazilian-market}}

\begin{longtable}[]{@{}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2727}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2386}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.0227}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2273}}
  >{\raggedright\arraybackslash}p{(\columnwidth - 8\tabcolsep) * \real{0.2386}}@{}}
\toprule\noalign{}
\begin{minipage}[b]{\linewidth}\raggedright
Brazilian Income (60\%)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Amount
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
US Income (40\%)
\end{minipage} & \begin{minipage}[b]{\linewidth}\raggedright
Amount
\end{minipage} \\
\midrule\noalign{}
\endhead
\bottomrule\noalign{}
\endlastfoot
Transfer Price & (700,000) & & Manufacturing Cost & (500,000) \\
Transport Cost & (200,000) & & Transfer Price & 700,000 \\
Sale Price & 1,000,000 & & \textbf{US PTOI} & \textbf{200,000} \\
\textbf{Brazilian PTOI} & \textbf{100,000} & & Taxes &
(200,000\(\times\).4) \\
Taxes & (100,000\(\times\).6) & & \textbf{US ATOI} & \textbf{120,000} \\
\textbf{Brazilian ATOI} & \textbf{40,000} & & & \\
& & & & \\
\textbf{V-G ATOI} & \textbf{160,000} & & & \\
\end{longtable}

\hypertarget{now-we-can-answer-3}{%
\subsection{Now we can answer 3}\label{now-we-can-answer-3}}

\begin{itemize}
\tightlist
\item
  We should manufacture the product and sell it in Switzerland.
\item
  The transfer price must be 500,000
\end{itemize}

\hypertarget{question-4}{%
\subsection{Question 4:}\label{question-4}}

\begin{itemize}
\tightlist
\item
  Now suppose each manager acts autonomously to maximize his or her own
  subsidiary's after-tax operating income, and the subsidiaries are
  given the freedom to negotiate their own transfer price.

  \begin{itemize}
  \tightlist
  \item
    Which subsidiary will get the product and at what price?
  \item
    Is your answer the same as your answer in 3? Explain why or why not.
  \end{itemize}
\end{itemize}

\hypertarget{imagine-the-auction-again}{%
\subsection{Imagine the auction
again:}\label{imagine-the-auction-again}}

\begin{enumerate}
\def\labelenumi{\arabic{enumi}.}
\tightlist
\item
  The optimal solution is for the US to get zero income. They will
  always prefer more income than is optimal for the firm.
\item
  The Swiss will pay up to 700,000 for the machine, even though it is
  sub-optimal for the company. So an auction that is limited to the
  prices allowed by taxes will not yield the optimal transfer price.
\end{enumerate}

\hypertarget{so-what-can-we-do}{%
\subsection{So what can we do?}\label{so-what-can-we-do}}

\begin{itemize}
\tightlist
\item
  Centralize the choice of transfer price, manufacturing, and sale.
\item
  Can you think of a set of rules that will produce the correct outcome?
\end{itemize}
